---
title: "5/7 Assignment"
author: "Jason Li"
date: "5/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Write a function to construct a confidence interval for a proportion. It should take arguments, p,
n, and a, where p is the sample proportion, n is the sample size, and a is the confidence level of
the test.**

```{r}
a = function(p, n, a){
  SE = sqrt(p*(1- p)/n)
  E = -qnorm(a/2)*SE
  c(p - E, p + E) 
}
a(5/24, 24, 0.05)
```

**(a) Use the ”ifelse” function to add a column of 1’s and 0’s to the data set, 1 for flights with number of passengers less than or equal to 315.**

```{r}
library(MASS)
a = ifelse(AirPassengers<=315, 1, 0)
table(a)
```

**(b) Use the column from part (a) to test the claim that the proportion of flights that include 315
passengers or less is 0.50. State the null and alternative hypotheses, results of test, and decision
you make.**

H0 x = 0.5;
Ha x != 0.5
Since p is close to Zero, I conclude that we reject the null hypothesis.

```{r}
y = 52
n = 144
Test =prop.test(y, n, p = 0.5, alternative = "two.sided", correct = FALSE)
Test
```

**(c) Find the 95% confidence interval for the proportion.**

```{r}
Test$conf.int
```

**(d)Now, test the claim that the mean number of passengers is 315. State the null and alternative
hypotheses, results of test, and decision you make. h0: mean = 0; ha: mean != 0;** 

Since the mean that I calculated below is not equal to 315, thus we reject the hypothesis. Also, the p value is close to zero
```{r}
b = t.test(AirPassengers, mu = 315)
b
```

**(e) Construct a 95% confidence interval for the mean.**
```{r}
b$conf.int
```

